---
knit: (function(input_file, encoding) {
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), 'index.html'))})
output: 
  html_document:
    theme: null
    highlight: null
    css: styles.css
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=9, fig.height=6, fig.align = 'left',
                      echo=FALSE, warning=FALSE, message=FALSE)
```

```{r echo = F, eval = T, include=F}
theme_plots <- function() {
  theme_minimal(base_family = "IBM Plex Sans Condensed") +
    theme(panel.grid.minor = element_blank(),
          plot.background = element_rect(fill = "white", color = NA),
          plot.title = element_text(face = "bold"),
          plot.subtitle = element_text(size=8),
          axis.title = element_text(face = "bold"),
          strip.text = element_text(face = "bold"),
          strip.background = element_rect(fill = "grey95", color = NA),
          legend.title = element_text(face = "bold"))
}

theme_plots_map <- function() {
  theme_minimal(base_family = "IBM Plex Sans Condensed") +
    theme(panel.grid.minor = element_blank(), panel.grid.major = element_blank(),
          axis.title.y = element_blank(), axis.title.x = element_blank(),
          axis.text.x = element_blank(), axis.text.y = element_blank(),
          strip.text.x = element_text(size = 10), legend.text = element_text(size=9), 
          legend.title = element_text(face="bold"), plot.title = element_text(face="bold"),
          plot.subtitle = element_text(size=8), aspect.ratio=1, legend.position="none")
}

my_date_format <- function()
{
  function(x)
  {
    m <- format(x,"%b")
    y <- format(x,"\n%Y")
    ifelse(duplicated(y),m,paste(m,y))
  }
}

names <- data.frame(as.factor(get_labels(polls$org)))
names <- separate(names, as.factor.get_labels.polls.org.., c("house", "method"), sep=",")
names$house <- as.factor(names$house)
housenames <- fct_recode(names$house, "Kantar" = "Kantar") %>%
  fct_collapse(., Kantar=c("Kantar"))
#names <- paste0(get_labels(housenames), collapse=", ")
names <- glue_collapse(get_labels(housenames), ", ", last = " and ")
polls$org <- str_replace_all(polls$org, "_", ", ")
```

# Pooling the Poles

```{r, echo=F, results='asis'}
cat("Pooled polls of intended voting at parliamentary elections in Poland, ", gsub(" 0", " ", format(Sys.time(), '%A %d %B')),".", sep="")
```

```{r, echo=F, results='asis'}
cat(str_c("Data from ", names, "."))
```

```{r, echo=F, results='asis'}
plotdraws <- add_fitted_draws(
  model = m1,
  newdata =
    tibble(time = today),
  re_formula = NA
) %>%
  group_by(.category) %>%
  mutate(.category = factor(.category,
                            levels = c("PiS", "KO", "Lewica", "Konfederacja", "Other", "TD"),
                            labels = c("PiS", "KO", "Lewica", "Konfederacja", "Other", "Trzecia Droga")))

medians <- plotdraws %>%
  summarise(est = median(.value)*100, .groups = "drop")

PiS.KO.diff <- plotdraws %>%
  pivot_wider(names_from=.category, values_from=.value) %>%
  mutate(., PiSKO = PiS-KO,
         PiSKO = sum((PiSKO > 0) / length(PiSKO)),
         PiSKO = round(PiSKO, 2)) %>%
  pull(PiSKO) %>%
  last(.)
```

## Latest estimates
\
Figures shown in white are median estimates of support per party. Undecided voters are excluded.

```{r, fig.align='center'}
add_fitted_draws(
    model = m1,
    newdata =
      tibble(time = today),
    re_formula = NA
  ) %>%
  group_by(.category) %>%
  mutate(.category = factor(.category,
                            levels = c("PiS", "KO", "Lewica", "Konfederacja", "Other", "TD"),
                            labels = c("PiS", "KO", "Lewica", "Konfederacja", "Other", "Trzecia Droga"))) %>%
  ggplot(aes(y=reorder(.category, dplyr::desc(-.value)), 
             x=.value, color=.category)) +
  geom_vline(aes(xintercept=0.05), colour="gray40", linetype="dotted") +
  stat_interval(aes(x=.value, color_ramp = stat(.width)), .width = ppoints(100)) %>%
  partition(vars(.category)) +
  scale_fill_manual(values=cols, guide=FALSE) +
  scale_color_manual(name=" ", values=cols, guide=FALSE) +
  ggdist::scale_color_ramp_continuous(range = c(1, 0), guide=FALSE) +
  scale_y_discrete(name="", position="right") +
  annotate(geom = "text", label=paste(round(medians$est[medians$.category=="PiS"],0)),
           y="PiS", x=medians$est[medians$.category=="PiS"]/100, size=4, hjust = "center", vjust=-1,
           family="IBM Plex Sans Condensed Light", color="black") +
  annotate(geom = "text", label=paste(round(medians$est[medians$.category=="KO"],0)),
           y="KO", x=medians$est[medians$.category=="KO"]/100, size=4, hjust = "center", vjust=-1,
           family="IBM Plex Sans Condensed Light", color="black") +
  annotate(geom = "text", label=paste(round(medians$est[medians$.category=="Trzecia Droga"],0)),
           y="Trzecia Droga", x=medians$est[medians$.category=="Trzecia Droga"]/100, size=4, hjust = "center", vjust=-1,
           family="IBM Plex Sans Condensed Light", color="black") +
  annotate(geom = "text", label=paste(round(medians$est[medians$.category=="Lewica"],0)),
           y="Lewica", x=medians$est[medians$.category=="Lewica"]/100, size=4, hjust = "center", vjust=-1,
           family="IBM Plex Sans Condensed Light", color="black") +
  annotate(geom = "text", label=paste(round(medians$est[medians$.category=="Konfederacja"],0)),
           y="Konfederacja", x=medians$est[medians$.category=="Konfederacja"]/100, size=4, hjust = "center", vjust=-1,
           family="IBM Plex Sans Condensed Light", color="black") +
  annotate(geom = "text", label=paste(round(medians$est[medians$.category=="Other"],0)),
           y="Other", x=medians$est[medians$.category=="Other"]/100, size=4, hjust = "center", vjust=-1,
           family="IBM Plex Sans Condensed Light", color="black") +
  annotate(geom = "text", label=paste("Pr(PiS > KO)  = ", PiS.KO.diff), y="PiS",
           x=quantile(plotdraws$.value[plotdraws$.category=="PiS"], 0.005), size=3.5, adj=c(1), family="IBM Plex Sans Condensed Light") +
  scale_x_continuous(breaks=c(0, 0.1, 0.2, 0.3, 0.4, 0.5), labels=c("0", "10", "20", "30", "40", "50")) +
  expand_limits(x = 0) +
  labs(x="") +
  theme_plots()
```

## Trends

```{r, fig.align='center'}
today <- interval(min(polls$midDate), Sys.Date())/years(1)

pred_dta <-
  tibble(
    time = seq(0, today, length.out = nrow(polls)),
    date = as.Date(time*365, origin = min(polls$midDate))
  )

pred_dta <-
  add_fitted_draws(
    model = m1,
    newdata = pred_dta,
    re_formula = NA
  ) %>%
  group_by(date, .category) %>%
  rename(party = .category) %>%
  mutate(
    party =
      party %>%
      factor(
        levels = c("PiS", "KO", "TD", "Lewica", "Konfederacja", "Other"),
        labels = c("PiS", "KO", "Trzecia Droga", "Lewica", "Konfederacja", "Other")
      )
  )

point_dta <-
  polls[names(polls) %in% c("midDate", "PiS", "KO", "Lewica", "Konfederacja", "Other", "TD")] %>%
  pivot_longer(
    cols = -midDate,
    names_to = "party",
    values_to = "est"
  ) %>%
  mutate(
    party =
      party %>%
      factor(
        levels = c("PiS", "KO", "TD", "Lewica", "Konfederacja", "Other"),
        labels = c("PiS", "KO", "Trzecia Droga", "Lewica", "Konfederacja", "Other")
      )
  )

ggplot() +
  geom_point(data=point_dta, aes(x = midDate, y = est, colour = party, fill=party), alpha = .5, size = 1, show.legend=FALSE) +
  #stat_lineribbon(data=pred_dta, aes(x = date, y = .value, color=party, fill=party), .width=c(0.95), alpha=1/2) +
  stat_lineribbon(data=pred_dta, aes(x = date, y = .value, color=party, fill=party), .width=c(0)) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  scale_x_date(date_breaks = "1 month",
               labels = my_date_format()) +
  coord_cartesian(xlim = c(min(polls$midDate), max(polls$midDate)),
                  ylim = c(0, .5)) +
  scale_color_manual(values=cols) +
  scale_fill_manual(values=cols, guide=FALSE) +
  labs(y = "", x="", color="", caption = "") +
  guides(colour = guide_legend(override.aes = list(alpha = 1, fill=NA))) +
  theme_plots()
```

## Estimated share of seats  
\
Mean estimated seat share with 95% credible intervals. Sum total may not equal 460.

```{r, fig.align='center'}
 ggplot(data=frame, mapping=aes(x=party, y=y, fill=party)) +
  geom_bar(stat="identity", width=.75, show.legend = F) +
  geom_abline(intercept=231, slope=0, colour="gray10", linetype=3) +
  geom_abline(intercept=276, slope=0, colour="gray10", linetype=3) +
  geom_abline(intercept=307, slope=0, colour="gray10", linetype=3) +
  scale_y_continuous('Number of seats', limits=c(0,320), breaks=c(0, 50, 100, 150, 200, 231, 276, 307)) +
  scale_fill_manual(name="Party", values = cols)+
  geom_label(aes(x=2, y=231), label="Legislative majority", size=3, adj=c(0), label.size=NA, fill="grey95", family="IBM Plex Sans Condensed Light") +
  geom_label(aes(x=2, y=276), label="Overturn presidential veto", size=3, adj=c(0), label.size=NA, fill="grey95", family="IBM Plex Sans Condensed Light") +
  geom_label(aes(x=2, y=307), label="Constitutional majority", size=3, adj=c(0), label.size=NA, fill="grey95", family="IBM Plex Sans Condensed Light") +
  annotate("text", x=frame$party, y=c(frame$y+18), label=frame$y, size=4, family="IBM Plex Sans Condensed Light")+
  annotate("text", x=frame$party, y=c(frame$y+8), label=paste("(",round(frame$ymin,0), "\u2013",round(frame$ymax,0),")", sep=""), size=3, family="IBM Plex Sans Condensed Light") +
  labs(x="", y="% of vote") +
  theme_plots()
```

## Constituency-level differences in share of seats for PiS and Koalicja Obywatelska
\
Constituencies in shades of blue have more PiS MPs; constituencies in orange have more KO MPs.

```{r echo = F, eval = T, include=F}
median_PiS <- ifelse(medians$est[medians$.category=="PiS"] >=5, medians$est[medians$.category=="PiS"], 0)
median_KO <- ifelse(medians$est[medians$.category=="KO"] >=5, medians$est[medians$.category=="KO"], 0)
median_Lewica <- ifelse(medians$est[medians$.category=="Lewica"] >=5, medians$est[medians$.category=="Lewica"], 0)
median_Konfederacja <- ifelse(medians$est[medians$.category=="Konfederacja"] >=5, medians$est[medians$.category=="Konfederacja"], 0)
`median_Trzecia Droga` <- ifelse(medians$est[medians$.category=="Trzecia Droga"] >=5, medians$est[medians$.category=="Trzecia Droga"], 0)
PiSpct <- round(weights$PiScoef*median_PiS, digits=2)
KOpct <- round(weights$KOcoef*median_KO, digits=2)
Lewicapct <- round(weights$Lewicacoef*median_Lewica, digits=2)
Konfederacjapct <- round(weights$Konfcoef*median_Konfederacja, digits=2)
`Trzecia Drogapct` <- round(weights$TDcoef*`median_Trzecia Droga`, digits=2)
MNpct <- c(0.12, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 5.37, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0)
KOest <- (weights$validvotes/100)*KOpct
PiSest <- (weights$validvotes/100)*PiSpct
Lewicaest <- (weights$validvotes/100)*Lewicapct
Konfederacjaest <- (weights$validvotes/100)*Konfederacjapct
`Trzecia Drogaest` <- (weights$validvotes/100)*`Trzecia Drogapct`
MNest <- (weights$validvotes/100)*MNpct
poldHondt <- data.frame(KO=rep(1,42), Konfederacja=rep(1,42), Lewica=rep(1,42),  MN=rep(1,42), PiS=rep(1,42), `Trzecia Droga`=rep(1,42))

for( i in 1 : 42 ) {
  poldHondt[i,] <- c(giveseats(v = c(KOest[i], Konfederacjaest[i], Lewicaest[i], MNest[i], PiSest[i], 
                                     `Trzecia Drogaest`[i]), ns = weights$magnitude[i], method="dh", thresh=5))$seats
}

#seats table
seats <- cbind(poldHondt, weights)
row.names(seats) <- weights$name
keep <- c("KO","Konfederacja","Lewica","MN", "PiS", "Trzecia Droga")
colnames(seats) <- c("KO", "Konfederacja","Lewica","MN", "PiS", "Trzecia Droga")
seats <- seats[keep]
seats <- seats[-1,]
seats$id <- 1:41
seats$PiSKO <-abs(seats$PiS-seats$KO)
seats$PiSmKO <- seats$PiS-seats$KO

#regional maps
const <- st_read('GRED_20190215_Poland_2011.shp')
const$id <- 0
const$id[const$cst==1] <- 24
const$id[const$cst==2] <- 27
const$id[const$cst==3] <- 4
const$id[const$cst==4] <- 7
const$id[const$cst==5] <- 28
const$id[const$cst==6] <- 34
const$id[const$cst==7] <- 25
const$id[const$cst==8] <- 26
const$id[const$cst==9] <- 29
const$id[const$cst==10] <- 36
const$id[const$cst==11] <- 31
const$id[const$cst==12] <- 33
const$id[const$cst==13] <- 37
const$id[const$cst==14] <- 40
const$id[const$cst==15] <- 13
const$id[const$cst==16] <- 12
const$id[const$cst==17] <- 22
const$id[const$cst==18] <- 1
const$id[const$cst==19] <- 6
const$id[const$cst==20] <- 14
const$id[const$cst==21] <- 35
const$id[const$cst==22] <- 21
const$id[const$cst==23] <- 10
const$id[const$cst==24] <- 38
const$id[const$cst==25] <- 39
const$id[const$cst==26] <- 16
const$id[const$cst==27] <- 17
const$id[const$cst==28] <- 30
const$id[const$cst==29] <- 23
const$id[const$cst==30] <- 18
const$id[const$cst==31] <- 11
const$id[const$cst==32] <- 32
const$id[const$cst==33] <- 41
const$id[const$cst==34] <- 15
const$id[const$cst==35] <- 5
const$id[const$cst==36] <- 19
const$id[const$cst==37] <- 20
const$id[const$cst==38] <- 2
const$id[const$cst==39] <- 3
const$id[const$cst==40] <- 8
const$id[const$cst==41] <- 9

label_points <- st_point_on_surface(const) %>%
  arrange(., id)
label_points <- st_coordinates(label_points) %>%
  as_tibble() %>%
  mutate(id = 1:n())
colnames(label_points) <- c("x","y","id")

plotdata <- merge(const, seats, by="id")
plotdata <- merge(plotdata, label_points, by="id")
```

```{r, fig.align='center', fig.width=12}
ggplot(plotdata)+
  geom_sf(aes(fill=as.integer(PiSmKO)))+
  theme(aspect.ratio=1) +
  #geom_label(aes(x=x, y=y, group=PiSmKO, label=PiSmKO), fill="white") +
  scale_fill_gradient2(name="PiSKO", limits=c(min=-20, max=20), low = "orange", mid="white", high = "blue", midpoint=0, guide="colorbar") +
  labs(title="Constituency-level differences in share of seats for PiS and Koalicja Obywatelska", subtitle="Constituencies in shades of blue have more PiS MPs; constituencies in orange have more KO MPs;\nconstituencies in white have equal numbers of PiS and KO MPs", 
       caption = "Ben Stanley (@BDStanley; benstanley.pl).") +
  theme_plots_map()
```

<!-- ## Trends by pollster   -->
<!-- \ -->
<!-- Only pollsters with more than five polls are included. -->

<!-- ```{r, fig.align='center', fig.width=12} -->
<!-- tab <- table(polls$org) -->
<!-- polls <- polls[polls$org %in% names(tab)[tab >= 5], ] -->

<!-- names <- data.frame(as.factor(get_labels(polls$org))) -->
<!-- names <- separate(names, as.factor.get_labels.polls.org.., c("house", "method"), sep="_") -->
<!-- names$house <- as.factor(names$house) -->
<!-- housenames <- fct_recode(names$house, "Kantar" = "Kantar") %>% -->
<!--   fct_collapse(., Kantar=c("Kantar")) -->
<!-- orgnames <- glue_collapse(get_labels(housenames), ", ", last = " and ") -->
<!-- polls$org <- str_replace_all(polls$org, "_", ", ") -->

<!-- today <- interval(min(polls$midDate), Sys.Date())/years(1) -->

<!-- pred_dta <- -->
<!--   tibble( -->
<!--     time = seq(0, today, length.out = nrow(polls)), -->
<!--     date = as.Date(time*365, origin = min(polls$midDate)), -->
<!--     org = polls$org, -->
<!--     pollster = polls$pollster -->
<!--   ) -->

<!-- pred_dta <- -->
<!--   add_fitted_draws( -->
<!--     model = m1, -->
<!--     newdata = pred_dta -->
<!--   ) %>% -->
<!--   group_by(date, .category, org) %>% -->
<!--   rename(party = .category) %>% -->
<!--   mutate( -->
<!--     party = -->
<!--       party %>% -->
<!--       factor( -->
<!--         levels = c("PiS", "KO", "Polska2050", "Lewica", "Konfederacja", "PSL", "Other"), -->
<!--         labels = c("PiS", "KO", "Polska 2050", "Lewica", "Konfederacja", "PSL", "Other") -->
<!--   ) -->
<!--   ) -->

<!-- point_dta <- polls %>% -->
<!--   select(org, midDate, PiS, KO, Lewica, Konfederacja, Other, PSL, Polska2050) %>% -->
<!--   pivot_longer( -->
<!--     cols = c(-midDate, -org), -->
<!--     names_to = "party", -->
<!--     values_to = "est" -->
<!--   ) %>% -->
<!--   mutate( -->
<!--     party = -->
<!--       party %>% -->
<!--       factor( -->
<!--         levels = c("PiS", "KO", "Polska2050", "Lewica", "Konfederacja", "PSL", "Other"), -->
<!--         labels = c("PiS", "KO", "Polska 2050", "Lewica", "Konfederacja", "PSL", "Other") -->
<!--       ) -->
<!--   ) -->

<!-- ggplot() + -->
<!--   geom_point(data=point_dta, aes(x = midDate, y = est, colour=party, fill=party), alpha = .5, size = 1, show.legend=FALSE) + -->
<!--   #stat_lineribbon(data=pred_dta, aes(x = date, y = .value, color=party, fill=party), .width=c(0.95), alpha=1/3) + -->
<!--   stat_lineribbon(data=pred_dta, aes(x = date, y = .value, color=party, fill=party), .width=c(0)) + -->
<!--   scale_y_continuous(labels = scales::percent_format(accuracy = 1)) + -->
<!--   scale_x_date(date_breaks = "3 month", -->
<!--                labels = my_date_format()) + -->
<!--   facet_wrap(~org, nrow=3) + -->
<!--   coord_cartesian(xlim = c(min(polls$midDate), max(polls$midDate)), -->
<!--                   ylim = c(0, .5)) + -->
<!--   scale_color_manual(values=cols) + -->
<!--   scale_fill_manual(values=cols, guide=FALSE) + -->
<!--   labs(y = "% of vote", x="", color="") + -->
<!--   theme_plots() + -->
<!--   guides(colour = guide_legend(override.aes = list(alpha = 1, fill=NA)))  -->
<!-- ``` -->

<!-- ## Latest figures by pollster   -->
<!-- \ -->
<!-- Only pollsters with more than five polls are included. -->

<!-- ```{r, fig.align='center', fig.width=12} -->
<!-- plotdraws <- polls %>%   -->
<!--   modelr::data_grid(time = today, pollster = pollster) %>% -->
<!--   add_fitted_draws(m1) -->

<!-- medians <- plotdraws %>% -->
<!--   summarise(est = median(.value)*100, .groups = "drop")  -->

<!-- names <- data.frame(as.factor(get_labels(polls$org))) -->
<!-- names$house <- as.factor(names$as.factor.get_labels.polls.org..) -->
<!-- names <- separate(names, as.factor.get_labels.polls.org.., sep=",", into=c('org', "label")) -->
<!-- orgnames <- glue_collapse(get_labels(sort(names$org)), ", ", last = " and ") -->

<!-- plot_latest_parl_pollster <- polls %>%   -->
<!--   modelr::data_grid(time = today, pollster = factor(pollster)) %>% -->
<!--   add_fitted_draws(m1) %>% -->
<!--   group_by(.category, pollster) %>% -->
<!--   mutate(.category = factor(.category, -->
<!--                             levels = c("PiS", "KO", "Lewica", "Konfederacja", "Other", "PSL", "Polska2050"), -->
<!--                             labels = c("PiS", "KO", "Lewica", "Konfederacja", "Other", "PSL","Polska 2050")), -->
<!--          pollster = factor(pollster, -->
<!--                            levels = get_labels(factor(polls$pollster)), -->
<!--                            labels = get_labels(factor(polls$org))) -->
<!--          ) %>% -->
<!--   ggplot(aes(y=reorder(.category, dplyr::desc(-.value)),  -->
<!--              x=.value, color=.category)) + -->
<!--   geom_vline(aes(xintercept=0.05), colour="gray40", linetype="dotted") + -->
<!--   stat_interval(aes(x=.value, color_ramp = stat(.width)), .width = ppoints(100)) %>% -->
<!--   partition(vars(.category)) + -->
<!--   scale_color_manual(values=cols, guide=FALSE) + -->
<!--   scale_fill_manual(values=cols, guide=FALSE) + -->
<!--   ggdist::scale_color_ramp_continuous(range = c(1, 0), guide=FALSE) + -->
<!--   scale_y_discrete(name="", position="right") + -->
<!--   scale_x_continuous(breaks=c(0, 0.1, 0.2, 0.3, 0.4, 0.5), labels=c("0", "10", "20", "30", "40", "50")) + -->
<!--   expand_limits(x = 0) + -->
<!--   facet_wrap(vars(pollster), ) + -->
<!--   labs(caption="Ben Stanley (@BDStanley; benstanley.pl).", x="", title="") + -->
<!--   theme_plots() -->

<!-- plot_latest_parl_pollster + -->
<!--   geom_text(data=medians %>% -->
<!--               mutate(.category = factor(.category, -->
<!--                                         levels = c("PiS", "KO", "Lewica", "Konfederacja", "Other", "PSL", "Polska2050"), -->
<!--                                         labels = c("PiS", "KO", "Lewica", "Konfederacja", "Other", "PSL","Polska 2050")), -->
<!--                      pollster = factor(pollster, -->
<!--                                        levels = get_labels(factor(polls$pollster)), -->
<!--                                        labels = get_labels(factor(polls$org))) -->
<!--               ),  -->
<!--             aes(x=est/100, y=.category, label=round(est,0)), check_overlap = TRUE, -->
<!--             size=3, hjust = 1.5, -->
<!--             family="IBM Plex Sans Condensed Light", color="black") -->
<!-- ``` -->
